analyze_growth

### 2024-10-09 smelt_2019_allseasons/analyze_growth.Rmd
Minor edits to organization of code - stick all FCCL together

# Effect of season at FCCL
```{r}
# CF
m1_FCCL <- lmer(deltaK ~ Season + (1|CageRep), data = FCCL_fish)
summary(m1_FCCL)
anova(m1_FCCL,type =2)
plot(m1_FCCL)

@@

##### FCCL
```{r}
# Weight
m1.FCCL.emm <- emmeans(m1_FCCL, "Season")
plotm1_FCCL = plot(m1.FCCL.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m1_FCCL = cld(m1.FCCL.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm1_FCCL) %>%
  mutate(.group = gsub(" ", "", .group)) %>% 
  mutate(Site = "FCCL")

letter_m1_emm_all <- rbind(letter_m1_FCCL, letter_m1)

@@

letter_m2_emm_all <- rbind(letter_m2_FCCL, letter_m2)
```

>>>>

@@

##### FCCL (for manuscript edits)

Models
```{r}
# CF
m1_FCCL <- lmer(deltaK ~ Season + (1|CageRep), data = FCCL_fish)
summary(m1_FCCL)
anova(m1_FCCL,type =2)
plot(m1_FCCL)

Emmeans
```{r}
# Weight
m1.FCCL.emm <- emmeans(m1_FCCL, "Season")
plotm1_FCCL = plot(m1.FCCL.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m1_FCCL = cld(m1.FCCL.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm1_FCCL) %>%
  mutate(.group = gsub(" ", "", .group)) %>% 
  mutate(Site = "FCCL")

@@

Join emmeans from RV with FCCL
```{r}
letter_m1_emm_all <- rbind(letter_m1_FCCL, letter_m1)
letter_m2_emm_all <- rbind(letter_m2_FCCL, letter_m2)
```
